---
title: "Assessment Two BUSA 2002 Group 9 - Clinical Result Callback Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(xts)
library(dygraphs)
library(plotly)
library(highcharter)
library(DT)
```

```{r data, include= FALSE}
data= read_csv("july_critical_callback_data.csv") %>%
  mutate(call_hour= hour(last_phone_datetime),
         call_wday= wday(last_phone_datetime, label= TRUE),
         call_date= day(last_phone_datetime),
         call_week= isoweek(last_phone_datetime),
         call_month= month(last_phone_datetime),
         call_year= year(last_phone_datetime),
         test_code= replace_na(test_code, "NA"))

```

Overall {data-icon="fa-phone-volume"}
===
Row
-----------------------------------------------------------------------

### Average Callback Time

```{r}
mean_tat= round(mean(data$call_tat), 0)
valueBox(value= mean_tat, icon= "fa-stopwatch", caption= "Average Callback Time", color= "lightblue")

```

### Total Calls

```{r}
total_calls= data %>% nrow()
valueBox(value= total_calls, icon= "fa-hashtag", caption= "Total Calls", color= "violet")

```

### Percent On Time

```{r}
num_ontime= data %>% filter(call_tat <= 30) %>% nrow()
num_late= data %>% filter(call_tat > 30) %>% nrow()
perc_ontime= round((num_ontime/total_calls)*100, 0)

if(perc_ontime >= 95){
  valueBox(value= perc_ontime, icon= "fa-percent", caption= "Percent on Time", color= "lightgreen")
} else{
  valueBox(value= perc_ontime, icon= "fa-percent", caption= "Percent on Time", color= "red")
}

```

Row
-----------------------------------------------------------------------

### Weekly Overview of Hourly Call Breakdown for `r date(min(data$last_phone_datetime))` to `r date(max(data$last_phone_datetime))`

```{r}
p1= ggplot(filter(data, call_wday %in% c("Mon", "Tue", "Wed", "Thu", "Fri"))) +
  geom_bar(aes(x= call_hour, fill= tech_location)) +
  facet_grid(call_wday~call_week) +
  labs(x= "Hour", y= "Count", fill= "Type") +
  scale_fill_manual(values= c("lightskyblue", "slategrey")) +
  theme_bw() +
  theme(legend.position = "top")

p1
```

### Daily Call Volumes `r date(min(data$last_phone_datetime))` to `r date(max(data$last_phone_datetime))`

```{r}
daily_vol= data %>%
  group_by(call_year, call_month, call_date) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  unite(dttm, call_year, call_month, call_date, sep = "-", remove= TRUE) %>%
  mutate(dttm= as.Date(dttm))

daily_vol_ts= xts(daily_vol$n, order.by= daily_vol$dttm)

p2= dygraph(daily_vol_ts, xlab= "Date", ylab= "Call Volume") %>%
  dyOptions(colors= "pink", strokeWidth = 2)
  
p2
  
```

Call Centre {data-icon="fa-users"}
===

Row
-----------------------------------------------------------------------

### Average Callback Time

```{r}
cc_calls= data %>% filter(tech_location == "CallCenter")
mean_tat_cc= round(mean(cc_calls$call_tat), 0)
valueBox(value= mean_tat_cc, icon= "fa-stopwatch", caption= "Average Callback Time", color= "lightblue")
```

### Total Calls

```{r}
total_cc_calls= data %>% filter(tech_location == "CallCenter") %>% nrow()
valueBox(value= total_cc_calls, icon= "fa-hashtag", caption= "Total Calls", color= "violet")

```

### Percent On Time

```{r}

cc_num_ontime= data %>% filter(tech_location =="CallCenter", call_tat <= 30) %>% nrow()
cc_num_late= data %>% filter(tech_location == "CallCenter",call_tat > 30) %>% nrow()
cc_perc_ontime= round((cc_num_ontime/total_cc_calls)*100, 0)

if(cc_perc_ontime >= 95){
  valueBox(value= cc_perc_ontime, icon= "fa-percent", caption= "Percent on Time", color= "lightgreen")
} else{
  valueBox(value= cc_perc_ontime, icon= "fa-percent", caption= "Percent on Time", color= "red")
}

```

Row
-----------------------------------------------------------------------

### Overdue Call Details for `r date(min(data$last_phone_datetime))` to `r date(max(data$last_phone_datetime))`

```{r}
cc_late= data %>% filter(tech_location == "CallCenter", call_tat > 30) %>%
  select(call_tat, accession, pt_type, pt_loc_code, test_code, result_datetime, phoned_title, tech)

datatable(cc_late, options= list(pageLength=20, autoWidth= TRUE))

```

### Tech Summary of Overdue Call Details for `r date(min(data$last_phone_datetime))` to `r date(max(data$last_phone_datetime))`

```{r}
p3= hcboxplot(
  outliers= FALSE, x= cc_calls$call_tat, var= cc_calls$tech, name= "TAT", color= "red", lineWidth= 2) %>%
  hc_title(text= "") %>%
  hc_xAxis(title= list(text= "Tech Code")) %>%
  hc_yAxis(title= list(text= "Call Time (minutes)")) %>%
  hc_chart(type= "column")

p3

```

Non Call Centre {data-icon="fa-users-slash"}
===

Row
-----------------------------------------------------------------------

### Average Callback Time

```{r}
ncc_calls= data %>% filter(tech_location == "Non-CC")
mean_tat_ncc= round(mean(ncc_calls$call_tat), 0)
valueBox(value= mean_tat_ncc, icon= "fa-stopwatch", caption= "Average Callback Time", color= "lightblue")
```


### Total Calls

```{r}
total_ncc_calls= data %>% filter(tech_location == "Non-CC") %>% nrow()
valueBox(value= total_ncc_calls, icon= "fa-hashtag", caption= "Total Calls", color= "violet")

```

### Percent On Time

```{r}

ncc_num_ontime= data %>% filter(tech_location =="Non-CC", call_tat <= 30) %>% nrow()
ncc_num_late= data %>% filter(tech_location == "Non-CC",call_tat > 30) %>% nrow()
ncc_perc_ontime= round((ncc_num_ontime/total_ncc_calls)*100, 0)

if(ncc_perc_ontime >= 95){
  valueBox(value= ncc_perc_ontime, icon= "fa-percent", caption= "Percent on Time", color= "lightgreen")
} else{
  valueBox(value= ncc_perc_ontime, icon= "fa-percent", caption= "Percent on Time", color= "red")
}

```


Row
-----------------------------------------------------------------------

### Overdue Call Details for `r date(min(data$last_phone_datetime))` to `r date(max(data$last_phone_datetime))`

```{r}
ncc_late= data %>% filter(tech_location == "Non-CC", call_tat > 30) %>%
  select(call_tat, accession, pt_type, pt_loc_code, test_code, result_datetime, phoned_title, tech)

datatable(ncc_late, options= list(pageLength=20, autoWidth= TRUE))

```


### Tech Summary of Overdue Call Details for `r date(min(data$last_phone_datetime))` to `r date(max(data$last_phone_datetime))`

```{r}
p3= hcboxplot(
  outliers= FALSE, x= ncc_calls$call_tat, var= ncc_calls$tech, name= "TAT", color= "red", lineWidth= 2) %>%
  hc_title(text= "") %>%
  hc_xAxis(title= list(text= "Tech Code")) %>%
  hc_yAxis(title= list(text= "Call Time (minutes)")) %>%
  hc_chart(type= "column")

p3

```
